Multi-target detection with application to cryo-electron microscopy

### 2019-06-17 InverseProblemsV2/inverse_problems_v2.tex
small change to abstract (to do -> of doing)

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ii}{\textbf{i}}
\newcommand{\jj}{\textbf{j}}
\newcommand{\Poisson}{\text{Poisson}}
\newcommand{\II}{\mathcal{I}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\mb}{\mathbf}
\newcommand{\mk}{\mathfrak}
\newcommand{\mc}{\mathcal}
\newcommand{\TODO}[1]{{\color{red}{[#1]}}}
\newcommand{\revised}[1]{{\color{magenta}{#1}}}
\newcommand{\R}{\mathbb{R}}
%\newcommand{\M}{\mathcal{M}}
\newcommand{\M}{m}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\L}{\mathcal{L}}

@@

We consider the multi-target detection problem of recovering a set of signals that appear 
multiple times at unknown locations in a noisy measurement.
In the low noise regime, one can estimate the signals by first detecting occurrences, then clustering and averaging them.
In the high noise regime, however, neither detection nor clustering can be performed reliably, so that strategies along these lines are destined to fail.  
Notwithstanding, using autocorrelation analysis, we show that the impossibility to detect and cluster signal occurrences in the presence of high noise does not necessarily preclude signal estimation.
Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals. These autocorrelations can be estimated accurately at any noise level given a sufficiently long measurement. 
%To recover the signals from the observed autocorrelations, we (heuristically) solve a set of polynomial equations through nonlinear least-squares. 
To recover the signals from the observed autocorrelations, we  solve a set of polynomial equations through nonlinear least-squares. 
We provide analysis regarding well-posedness of the task, and demonstrate numerically the effectiveness of the method in a variety of settings.

@@

\bibliographystyle{plain}
\bibliography{ref}

>>>>

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ii}{\textbf{i}}
\newcommand{\jj}{\textbf{j}}
\newcommand{\Poisson}{\text{Poisson}}
\newcommand{\II}{\mathcal{I}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\mb}{\mathbf}
\newcommand{\mk}{\mathfrak}
\newcommand{\mc}{\mathcal}
\newcommand{\TODO}[1]{{\color{red}{[#1]}}}
%\newcommand{\revised}[1]{{\color{magenta}{#1}}}
\newcommand{\revised}[1]{{\color{black}{#1}}}
\newcommand{\R}{\mathbb{R}}
%\newcommand{\M}{\mathcal{M}}
\newcommand{\M}{m}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\L}{\mathcal{L}}

@@

We consider the multi-target detection problem of recovering a set of signals that appear 
multiple times at unknown locations in a noisy measurement.
In the low noise regime, one can estimate the signals by first detecting occurrences, then clustering and averaging them.
In the high noise regime, however, neither detection nor clustering can be performed reliably, so that strategies along these lines are destined to fail.  
Notwithstanding, using autocorrelation analysis, we show that the impossibility of detecting and clustering signal occurrences in the presence of high noise does not necessarily preclude signal estimation.
Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals. These autocorrelations can be estimated accurately at any noise level given a sufficiently long measurement. 
%To recover the signals from the observed autocorrelations, we (heuristically) solve a set of polynomial equations through nonlinear least-squares. 
To recover the signals from the observed autocorrelations, we  solve a set of polynomial equations through nonlinear least-squares. 
We provide analysis regarding well-posedness of the task, and demonstrate numerically the effectiveness of the method in a variety of settings.

@@

\bibliographystyle{plain}
%\bibliography{ref}
\input{inverse_problems_v2.bbl}
